### 2022-12-10 dissertation/chapters/09-conclusion.tex
💚 Dedicated to Taylah, Beané & Aleah

\begin{itemize}
      \item A literature study was conducted on all related topics that are relevant to the development of the \acs{BHH} and is provided in Chapters ~\ref{chap:anns} to \ref{chap:probability}. The literature study included background information on \acs{ANN}, existing low-level \index{heuristic}heuristics, meta-learning, \acp{HH}, probability theory, and Bayesian statistics. Detailed discussions were provided on every topic and was supported by visual illustrations and mathematical derivations.

>>>>

\begin{itemize}
      \item A literature study was conducted on all related topics that are relevant to the development of the \acs{BHH} and is provided in Chapters \ref{chap:anns} to \ref{chap:probability}. The literature study included background information on \acs{ANN}, existing low-level \index{heuristic}heuristics, meta-learning, \acp{HH}, probability theory, and Bayesian statistics. Detailed discussions were provided on every topic and was supported by visual illustrations and mathematical derivations.
